(Deep) Induction for GADTs\vspace*{-0.1in}

### 2021-04-21 induction-paper/ENTCS-GADT-induction.tex
test

This paper extends deep induction to a robust class of GADTs that are
not truly nested. It also shows that truly nested GADTs do not admit
deep induction rules. Our development is implemented in Agda, as is a
case study showing how deep induction can prove properties of GADTs
that are not provable by structural induction.\looseness=-1

>>>>

This paper extends deep induction to a robust class of GADTs that are
not truly nested. It also shows that truly nested GADTs do not admit
deep induction rules. Our development is implemented in Agda, as is a
case study showing how deep induction can prove properties of GADTs
that are not provable just by structural induction.\looseness=-1
